### 2016-09-30 architecture.tex
Remove redundant word

In SymPy every symbolic expression is an instance of a Python \texttt{Basic}
class,\footnote{Some
  internal classes, such as those used in the polynomial submodule, do not follow
  this rule for efficiency reasons.} a superclass of all SymPy types providing
common methods to all SymPy tree-elements, such as traversals.  The children of a node in the
tree are held in the \texttt{args} attribute.  A terminal or leaf node in the
expression tree has empty \texttt{args}.

>>>>

In SymPy every symbolic expression is an instance of the class
\texttt{Basic},\footnote{Some internal classes, such as those used in the
  polynomial submodule, do not follow this rule for efficiency reasons.} a
superclass of all SymPy types providing common methods to all SymPy
tree-elements, such as traversals. The children of a node in the tree are held
in the \texttt{args} attribute. A terminal or leaf node in the expression tree
has empty \texttt{args}.
